---
title: "RWorksheet_Salinas#4c.Rmd."
author: "Reysha Marie S. Salinas"
date: "2023-11-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. a. Show your solutions on how to import a csv file into the environment.
```{r}
library(readr)
mpg <- read_csv("mpg.csv")
View(mpg)
```


1b. Which variables from mpg dataset are categorical?
```{r}
ctgr <- names(sapply(mpg, is.factor))
print(ctgr)

```

1c. Which are continuous variables?
```{r}
conti <- names(sapply(mpg, is.numeric))
print(conti)
```


2. Which manufacturer has the most models in this data set? Which model has the most variations?
Show your answer.
```{r}


``` 



2 a. Group the manufacturers and find the unique models. Show your codes and result.
```{r}
model <- unique(mpg[, c("manufacturer", "model")])
count <- table(model$manufacturer) 
print(count)
```


2 b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r}

print(paste("Manufacturer with the most models:", model))

barplot(count, main = "Number of Models by Manufacturer",
        xlab = "Manufacturer", ylab = "Number of Models",
        col = "pink", 
        las = 2)

ggplot(data = data.frame(manufacturer = names(count)),
count = as.numeric(count))
x = "Manufacturer"
y = "Number of Models"

```


2. Same dataset will be used. You are going to show the relationship of the model and the manufacturer

```{r}
correlation[model$manufacturer] 

```