---
title: "RWorksheet_Salinas#4b"
author: "Reysha Marie S. Salinas"
date: "2023-11-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

```{r} 

vectorA <- c(1,2,3,4,5)

matrixA <- matrix(c(0,0,0,0,0), nrow = 5,  ncol = 5)

for (i in 1:5){
for(k in 1:5){
if (i == k){
matrixA[i,k] <- vectorA[i] 
} 
}
}
abs(matrixA) 

```  

2. Print the string "*" using for() function. The output should be the same as shown
in Figure 1.
```{r name, echo = TRUE}
for(i in 1:5) {
  numb <- rep("*", i)
  print(numb)
}
```


3. Get an input from the user to print the Fibonacci sequence starting from the 1st input
up to 500. Use repeat and break statements. Write the R Scripts and its output. 

```{r}


start_num <- as.numeric(readline("Enter the starting number for the Fibonacci sequence: "))

num1 <- 0
num2 <- 1

repeat {
  if (num1 >= start_num && num1 <= 500) {
    cat(num1, " ")
  }
  fib_sum <- num1 + num2
  num1 <- num2
  num2 <- fib_sum
  
  if (num1 > 500) {
    break
  }
  cat(\n)
}



```

4  Import the dataset as shown in Figure 1 you have created previously.

4. A  What is the R script for importing an excel or a csv file? Display the first 6 rows of the dataset? Show your codes and its result. 
```{r}
imprt <- read.csv("Household.csv")
head(imprt)
``` 


4. B Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.

```{r}
males <- Household[Household$Gender == "M",]
males

females <- Household[Household$Gender == "F",]
females

observationF <- nrow(females)
observationM <- nrow(males)

observationF 
observationM
```  

4. C Create a graph for the number of males and females for Household Data. Use plot(),
chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
its result. 

```{r}

total <- table(Household$Gender)
barplot(total,
        main = "Number of Males and Females", xlab = "Gender", ylab = "Count", col = c("black", "violet"),  legend.text = rownames(total),beside = TRUE)
```

5. The monthly income of Dela Cruz family was spent on the following: 

5. A Create a piechart that will include labels in percentage.Add some colors and title of
the chart. Write the R scripts and show its output. 

```{r}
spend <- data.frame(
  Category = c("Food", "Electricity", "Savings", "Miscellaneous"),
  Value = c(60, 10, 5, 25)
)

spend$Percentage <- spend$Value / sum(spend$Value) * 100
colors <- c("brown", "pink", "yellow", "violet")

# Adjust the font size with the cex parameter
pie(spend$Value,
    labels = paste(spend$Category, " (", spend$Percentage, "%)"),
    col = colors, 
    main = "The Monthly Income Spending of Dela Cruz Family",
    cex = 0.8) 

legend("topleft", spend$Category, fill = colors)


```
6. Use the iris dataset. 

A. Check for the structure of the dataset using the str() function. Describe what you
have seen in the output.
```{r}  

str(iris)  

```
I was curious and made a research about this. The output of the code provides information about the iris dataset, which is renowned for its use in data analysis and machine learning. It reveals the following details:

1. The dataset comprises 150 observations and 5 variables.
2. 'Sepal.Length' represents the sepal length of iris flowers.
3. 'Sepal.Width' represents the sepal width of iris flowers.
4. 'Petal.Length' signifies the petal length of iris flowers.
5. 'Petal.Width' signifies the petal width of iris flowers. 
6. 'Species' This is the categorized variables. 




B. Create an R object that will contain the mean of the sepal.length,
sepal.width,petal.length,and petal.width. What is the R script and its result?
```{r}

value_of_means <- c(
  Lsepal <- mean(iris$Sepal.Length),
  Wsepal <- mean(iris$Sepal.Width) ,
  Lpetal <- mean(iris$Petal.Length), 
  Wpetal <- mean(iris$Petal.Width) 
) 
value_of_means
```






C.Create a pie chart for the Species distribution. Add title, legends, and colors. Write
the R script and its result.
```{r}
# Assuming 'iris' is the name of your dataset
species <- table(iris$Species)
colors <- c("pink", "gray", "brown")

# Create the pie chart
pie(species, col = colors, labels = species )
legend("topright", legend = levels(iris$Species), fill = colors)
title("Species Distribution")

```


D. Subset the species into setosa, versicolor, and virginica. Write the R scripts
and show the last six (6) rows of each species.

```{r}
#subset 

setosa_subset <- iris[iris$Species == "setosa" ,]
versicolor_subset <- iris[iris$Species == "versicolor",]
virginica_subset <- iris[iris$Species == "virginica",] 

#last 6 row each 

tail(setosa_subset, 6) 
tail(versicolor_subset, 6)
tail(virginica_subset, 6) 
``` 

E. Create a scatterplot of the sepal.length and sepal.width using the different
species(setosa,versicolor,virginica). Add a title = “Iris Dataset”, subtitle = “Sepal
width and length, labels for the x and y axis, the pch symbol and colors should be based on
the species.

Hint: Need to convert to factors the species to store categorical variables.

```{r}
library(ggplot2)

#  factor
iris$Species <- as.factor(iris$Species)

# Create a scatterplot
scatterplot <- ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species, shape = Species)) +
  geom_point(size = 5) +
  labs(
    title = "Iris Dataset",
    subtitle = "Sepal Width and Length",
    x = "Sepal Length",
    y = "Sepal Width"
  ) +
  scale_color_manual(values = c("setosa" = "brown", "versicolor" = "pink", "virginica" = "violet")) +
  scale_shape_manual(values = c("setosa" = 2, "versicolor" = 18, "virginica" = 9))

print(scatterplot)

``` 


F. Interpret the result.



7 
```{r}
alexa_file <- read_excel("alexa_file.xlsx")
View(alexa_file) 
```

A. Rename the white and black variants by using gsub() function.
```{r}
alexa_file$variation <- gsub("Black Dot", "New Name", alexa_file$variation) 
alexa_file$variation <- gsub("White Dot", "Reysha Marie", alexa_file$variation) 

knitr::include_graphics("alexa_file.xlsx")
```