---
title: "RWorksheet_Salinas#4b"
author: "Reysha Marie S. Salinas"
date: "2023-11-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  Using the for loop, create an R script that will display a 5x5 matrix as shown in
Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero matrix.

```{r} 

vectorA <- c(1,2,3,4,5)

matrixA <- matrix(c(0,0,0,0,0), nrow = 5,  ncol = 5)

for (i in 1:5){
for(k in 1:5){
if (i == k){
matrixA[i,k] <- vectorA[i] 
} 
}
}
abs(matrixA) 

```  

2. Print the string "*" using for() function. The output should be the same as shown
in Figure 1.
```{r name, echo = TRUE}
for(i in 1:5) {
  numb <- rep("*", i)
  print(numb)
}
```


3. Get an input from the user to print the Fibonacci sequence starting from the 1st input
up to 500. Use repeat and break statements. Write the R Scripts and its output. 

```{r}
 

userInput <- as.integer(readline("Enter starting number for Fibonacci sequence: "))

x <- userInput
y <- 0


cat("Fibonacci sequence starting from", userInput, ":\n")

repeat {
  
  next_num <- x + y
  
  if (next_num > 500){
    break
  }
  cat(next_num, " ")
  x <- y
  y <- next_num
  
}

```

4  Import the dataset as shown in Figure 1 you have created previously.

4. A  What is the R script for importing an excel or a csv file? Display the first 6 rows of the dataset? Show your codes and its result. 
```{r}
imprt <- read.csv("Household.csv")
head(imprt)
``` 


4. B Create a subset for gender(female and male). How many observations are there in
Male? How about in Female? Write the R scripts and its output.

```{r}
males <- Household[Household$Gender == "M",]
males

females <- Household[Household$Gender == "F",]
females

observationF <- nrow(females)
observationM <- nrow(males)

observationF 
observationM
```  

4. C Create a graph for the number of males and females for Household Data. Use plot(),
chart type = barplot. Make sure to place title, legends, and colors. Write the R scripts and
its result. 

```{r}

total <- table(Household$Gender)
barplot(total,
        main = "Number of Males and Females", xlab = "Gender", ylab = "Count", col = c("black", "violet"),  legend.text = rownames(total),beside = TRUE)
```

5. The monthly income of Dela Cruz family was spent on the following: 

5. A Create a piechart that will include labels in percentage.Add some colors and title of
the chart. Write the R scripts and show its output. 

```{r}
spend <- data.frame(
  Category = c("Food", "Electricity", "Savings", "Miscellaneous"),
  Value = c(60, 10, 5, 25)
)

spend$Percentage <- spend$Value / sum(spend$Value) * 100
colors <- c("brown", "pink", "yellow", "violet")

# Adjust the font size with the cex parameter
pie(spend$Value,
    labels = paste(spend$Category, " (", spend$Percentage, "%)"),
    col = colors, 
    main = "The Monthly Income Spending of Dela Cruz Family",
    cex = 0.8) 

legend("topleft", spend$Category, fill = colors)


```

```{r} 

```