---
title: "RWorksheet_5.Rmd"
author: "Reysha Marie S. Salinas"
date: "2023-12-21"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Basic Statistics
1. Create a data frame for the table below. Show your solution.

```{r}
Stud <- c(1,2,3,4,5,6,7,8,9,10)
Pre_Test <- c(55,54,47,57,51,61,57,54,63,58)
Post_Test <-c(61,60,56,63,56,63,59,56,62,61)

Student_Score <- data.frame(
  Student = Stud, 
  Pre_Test = Pre_Test, 
  Post_Test =Post_Test
)

Student_Score
```


a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.

```{r}
library(Hmisc)

#RESULT
summary(Student_Score)

```


```{r}
library(pastecs)


#RESULT
stat.desc(Student_Score)

```


2. The Department of Agriculture was studying the effects of several levels of a fertilizer
on the growth of a plant. For some analyses, it might be useful to convert the fertilizer
levels to an ordered factor.
```{r}



fertilizer_levels <- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)
ordered_factor <- ordered(fertilizer_levels)
ordered_factor


#The ordered_factor will have the levels ordered as 10, 20, 50, reflecting the specified order.
```


3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the ex-
ercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”,

“n”, “i”, “l” ; n=none, l=light, i=intense
a. What is the best way to represent this in R?

```{r}
subjects <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")

subjects_factor <- factor(subjects, levels=c("n", "l", "i"))
subjects_factor


```


4. Sample of 30 tax accountants from all the states and territories of Australia and their
individual state of origin is specified by a character vector of state mnemonics


```{r}

state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
```

a. Apply the factor function and factor level. Describe the results.

```{r}
state_factor <- factor(state)

summary(state_factor)
#We can see how many times each state appears in the given sample.
```


```{r}
state_levels <- c("nsw", "vic", "qld", "wa", "sa", "tas", "nt", "act")

state <- factor(state, levels = state_levels)

summary(state)
#Provide a simple count of occurrences for each level in the order you specified. 

```

5. From #4 - continuation:
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")
incmeans <- tapply(incomes, state, mean)
incmeans
```

b. Copy the results and interpret.

The median income values across different states and territories in Australia are as follows: In the ACT, the median income is $44,500, while in  NSW accountants have a median income of $57,333.33. In the NT, the median income is $55,500, and in QLD, accountants have a median income of $53,600. SA reports a median income of $55,000, while in TAS, accountants have a median income of $60,500. In VIC, the median income is $56,000, and accountants in WA earn a median income of $52,250. These figures offer insights into the central income tendencies for accountants in each region.


```{r}
#-------------------------------------------------------------------
```


6. Calculate the standard errors of the state income means (refer again to number 3)

```{r}
#------------------------------------------------------------------

stdError <- function(x) sqrt(var(x)/length(x))

incster <- tapply(incomes, state, stdError)

print(incster)
```

a. What is the standard error? Write the codes.

```{r}

mean_incomes <- tapply(incomes, state, mean)


std_incomes <- tapply(incomes, state, sd)

n_incomes <- tapply(incomes, state, length)

stdError <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, state, stdError)

print(incster)

```

b. Interpret the result.

ACT boasts stability at 1.5, while NSW stands strong at 4.31. NT and QLD follow with scores of 4.5 and 4.11, indicating robust economic activity. SA scores 2.74, TAS registers 0.5, and VIC leads at 5.24, showcasing economic strength. WA maintains a solid standing at 2.66. These scores provide a succinct overview, aiding in targeted interventions and policy considerations.
```{r}
#------------------------------------------------------------------
```

7. Use the titanic dataset.

```{r}
data("Titanic")

print(Titanic)
```


a. subset the titatic dataset of those who survived and not survived. Show the codes
and its result.
```{r}

data("Titanic")

no_survived_adult <- as.vector(Titanic[, , "Adult", "No"])
no_survived_child <- as.vector(Titanic[, , "Child", "No"])
yes_survived_adult <- as.vector(Titanic[, , "Adult", "Yes"])
yes_survived_child <- as.vector(Titanic[, , "Child", "Yes"])

cat("Number of Adults who did not survive:", sum(no_survived_adult), "\n")
cat("Number of Children who did not survive:", sum(no_survived_child), "\n")
cat("Number of Adults who survived:", sum(yes_survived_adult), "\n")
cat("Number of Children who survived:", sum(yes_survived_child), "\n")


```
8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically
as Dr. Wolberg reports his clinical cases. The database therefore reflects this

a. describe what is the dataset all about.

The dataset focuses on women facing breast cancer and involves a survey scale ranging from 1 to 10. This scale is used to assess various characteristics of cell nuclei present in breast cancer, such as clump thickness, size uniformity, shape uniformity, marginal adhesion, epithelial size, bare nucleoli, bland chromatin, normal nucleoli, and mitoses. Each score on the scale reflects the severity or abnormality of the respective characteristic. The dataset aims to capture and analyze these features to gain insights into the nature of breast cancer in the surveyed women.

```{r}
#---------------------------------------------------------
```

d. Compute the descriptive statistics using different packages. Find the values of:
d.1 Standard error of the mean for clump thickness.

```{r}
data <- read.csv('breastcancer_wisconsin.csv')

clump_thickness_column <- data$clump_thickness
std_error <- sd(clump_thickness_column) / sqrt(length(clump_thickness_column))

print(std_error)


```

d.2 Coefficient of variability for Marginal Adhesion.

```{r}
data <- read.csv('breastcancer_wisconsin.csv')

marginal_adhesion_column <- data$marginal_adhesion
coefficient_of_variability <- sd(marginal_adhesion_column) / mean(marginal_adhesion_column) * 100

print(coefficient_of_variability)

```

d.3 Number of null values of Bare Nuclei.

```{r}
data <- read.csv('breastcancer_wisconsin.csv')

bare_nucleoli_column <- data$bare_nucleoli
null_values_count <- sum(is.na(bare_nucleoli_column))


print(null_values_count)

```

d.4 Mean and standard deviation for Bland Chromatin
```{r}
mean_bland_chromatin <- mean(data$bland_chromatin, )
sd_bland_chromatin <- sd(data$bland_chromatin, )

print(paste("Mean:", mean_bland_chromatin))
print(paste("Standard deviation:", sd_bland_chromatin))
```

d.5 Confidence interval of the mean for Uniformity of Cell Shape
```{r}
data <- read.csv('breastcancer_wisconsin.csv')
shape_uniformity <- data$shape_uniformity

result <- t.test(shape_uniformity)

cat("Mean:", result$estimate, "\n")
cat("95% confidence interval:", result$conf.int[1], result$conf.int[2], "\n")



```


```{r}
#----------------------------------------
```

d. How many attributes?
```{r}
data <- read.csv('breastcancer_wisconsin.csv')

num_attributes <- length(names(data))
print(num_attributes)

```


e. Find the percentage of respondents who are malignant. Interpret the results.
```{r}
data <- read.csv('breastcancer_wisconsin.csv')


malignant_count <- sum(data$class == "malignant")
total_count <- nrow(data)

percentage_malignant <- (malignant_count / total_count) * 100
print(percentage_malignant)


```

9. Export the data abalone to the Microsoft excel file. Copy the codes.
install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")
view(abalone)
head(abalone)
summary(abalone)

```{r}

install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")

data("abalone")

head(abalone)
summary(abalone)

```